Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-04 paper.tex
Renamed the figures' names

% Explain all sampling techniques (maybe rename 4, 5, and 6)
% 1. random unreal (baseline)
\paragraph{Random unreal}
The training set is sampled randomly with no restriction, that is,
regardless of their generation time.  This method will be used as a
baseline for comparison with other methods, although it is not
realistic.
\begin{figure}
\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training_plot}
  \caption{Sample training set of random Unreal method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}

% 2. columns
\paragraph{Complete columns}
The training set is sampled by randomly selecting complete columns in
the matrix, that is, complete subject executions. The last selected
column might be incomplete to meet the exact training ratio. This
method is realistic: it corresponds to a situation where the
collaborative filtering method will predict the reproducibility in the
remaining subjects from the subjects in the training set.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training_plot}
  \caption{Sample training set of Columns method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}
% 3. rows
\paragraph{Complete rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files in
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a
situation where the processing of all the subjects is launched and
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the
remaining files.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training_plot}
  \caption{Sample training set of Rows method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}

% 4. random real
\paragraph{Random real (Uniform-S)}
\todo{Explain this better}The training set sampling in this method is quite simillar to rows method.
The key difference lies in the way that the next subject is selected randomly. In this respect, subjects' files
are selected by coming their turn which is defined according to their generation time in the pipeline.
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training_plot}
  \caption{Sample training set of random Real method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}

>>>>

% Explain all sampling techniques (maybe rename 4, 5, and 6)
% 1. random unreal (baseline)
\paragraph{Random unreal}
The training set is sampled randomly with no restriction, that is,
regardless of their generation time.  This method will be used as a
baseline for comparison with other methods, although it is not
realistic.
\begin{figure}
\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training}
  \caption{Sample training set of random Unreal method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}

% 2. columns
\paragraph{Complete columns}
The training set is sampled by randomly selecting complete columns in
the matrix, that is, complete subject executions. The last selected
column might be incomplete to meet the exact training ratio. This
method is realistic: it corresponds to a situation where the
collaborative filtering method will predict the reproducibility in the
remaining subjects from the subjects in the training set.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training}
  \caption{Sample training set of Columns method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}
% 3. rows
\paragraph{Complete rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files in
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a
situation where the processing of all the subjects is launched and
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the
remaining files.
\begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training}
  \caption{Sample training set of Rows method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}

% 4. random real
\paragraph{Random real (Uniform-S)}
\todo{Explain this better}The training set sampling in this method is quite simillar to rows method.
The key difference lies in the way that the next subject is selected randomly. In this respect, subjects' files
are selected by coming their turn which is defined according to their generation time in the pipeline.
\begin{figure}
 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training}
  \caption{Sample training set of random Real method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
  \label{fig:Sample Training set }
\end{figure}
